\begin{thebibliography}{1}

\bibitem{violaJones}Paul Viola and Michael Jones. Robust real-time face detection. International Journal of Computer Vision, 57(2):137-154, 2004.

\bibitem{exampleUse}Star Trinity,(2014), Face detection applications [Online], Available: http://startrinity.com/VideoRecognition/FaceDetection/FaceDetectionApplications.aspx  [17 November 2014].

\bibitem{faceCode}Real Python,(2014), Face Detection in Python Using a Webcam [Online], Available: https://realpython.com/blog/python/face-detection-in-python-using-a-webcam/ [17 November 2014].

\bibitem{violaJonesSnow}Paul Viola,Michael Jones and Daniel Snow. Detecting Pedestrians Using Patterns of Motion and Appearance. International Journal of Computer Vision, 63(2):153–161, 2005.

\bibitem{banana}Thorsten Ball, (2013), Train your own OpenCV Haar Classifier [Online], Avaliable: http://coding-robin.de/2013/07/22/train-your-own-opencv-haar-classifier.html [17 November 2014].

\bibitem{dalalTriggs}Navneet Dalal and Bill Triggs. Histograms of Oriented Gradients for Human Detection. Available: http://lear.inrialpes.fr/people/triggs/pubs/Dalal-cvpr05.pdf [17 November 2014].

\bibitem{book}Richard Szeliski,(2010), Computer Vision: Algorithms and Applications, pp. 655-684 .

\bibitem{motionDetection} Pablo Rivas and Mario I. Chacón.  Real time motion detection for fast human identification based on face recognition. CIECE – CITEE, 2006.

\bibitem{occlusions}Aisha Azeem, Muhammad Sharif, Mudassar Raza and Marryam Murtaza. A Survey: Face Recognition Techniques under Partial Occlusion. The International Arab Journal of Information Technology, Vol. 11, No. 1, January 2014.

\bibitem{specularRefelection}The Physics class room. Specular vs. Diffuse Reflection. Available: http://www.physicsclassroom.com/class/refln/Lesson-1/Specular-vs-Diffuse-Reflection [20 November 2014].

\bibitem{faceRec}Vincent Christlein, Christian Riess, Elli Angelopoulou and Georgios Evangelopoulos and Ioannis A. Kakadiaris. The Impact of Specular Highlights on 3D-2D Face Recognition. Available: http://web.mit.edu/gevang/www/papers/Christlein\_SpecularHighlights\_SPIE13/Christlein\_Specular Highlights\_SPIE13.pdf [20 November 2014].

\end{thebibliography}